Where Do Events Come From?

### 2018-08-04 paper.tex
...

TODO: weakness

@@

@@

- TinyOS
    - async, race condition avoidance
        - nesc manual
    - ICEM, standby
        - icem paper

@@

@@

%% Bibliography
\bibliography{my,other}

%% Appendix
\appendix
\section{Appendix}

Text of appendix \ldots

>>>>

Our work is largely inspired by TinyOS~\cite{wsn.tos}, a low-power OS for
wireless devices, which also provides asynchronous events with a compile-time
data race detector~\cite{wsn.nesc}, and automatic energy management triggered
from idle CPU states~\cite{wsn.icem}.
%
We adapted these ideas to the structured reactive programming model of \CEU,
and refined them with stronger guarantees due to lexical scope and automatic
finalization.

@@

TODO: energy savings

@@

Our work is largely inspired by TinyOS~\cite{wsn.tos} and its companion
language nesC~\cite{wsn.nesc}, which is a callback-driven dialect of C.
%
By default, callbacks are synchronous but can be annotated as \code{async} when
triggered directly from interrupts.
In this case, a static data-race detector ensures that concurrent accesses are
protected by atomic sections.
%
Since the TinyOS runtime is also based on an event loop, it can easily detect
idle periods and put the CPU to sleep.
Device drivers also cooperate with the runtime to designate the best sleep
mode~\cite{wsn.icem}.

In comparison to nesC, our proposal takes advantage of the structured
mechanisms of \CEU to offer even stronger guarantees.
%
For instance, nesC cannot provide a safe abortion mechanism, since the notion
of control flow is entirely dynamic, typically encoded inside ordinary global
variables that represent state machines.
%
For this reason, some manual bookkeeping is required to avoid that resources
eventually leak (e.g., memory or energy).
As an example, if the result of a long chain of split-phase I/O is no longer
required due to a cancellation event, the cancellation callback is itself
responsible for aborting the ongoing unnecessary operations.
%
\CEU relies on the \code{par/or} and \code{finalize} structured mechanisms to
manage resources automatically.

@@

- artigo synchronous languages

- shim

- electre

@@

\bibliography{my,other}
